### 2021-03-17 paper/localpsf.tex
more advanced weighting function interpolation could fix boundary issues

\begin{itemize}
	\item GLR vs PCH diffusion time (H)
	\item GLR vs PCH number of obs (Computational cost) (S)
	\item GLR vs PCH aspect ratio (CC) (S)
	\item mesh scalability of PCH (CC) (H)
	\item spectrum plots $P^{-1} H - I$ (Quality of approximation) (H, not Stokes?)
	\item number of krylov iterations: reg precond vs PCH (where?) (H)
	\item turn on preconditioner after number of krylov iterations exceeds 15 in an iteration. Rebuild "as needed". (H)
	\item $P - H = USV^T$ <- less good
	\item $P^{-1} H - I = USV^T$ <- better
	\item true parameter (H)
	\item deterministic reconstruction (H)
	\item noisy measurements (1\% noise). $u|_\text{top}$ (H)
	\item recovered state at top (H)
\end{itemize}

>>>>

\textbf{Heat equation}
\begin{itemize}
	\item Hessian per-column error plots for 1, 5, and 15 batches
	\item $H-P$ error vs number of batches for interior and whole domain
	\item $P^{-1}H-I$: error vs rank for $P=R$ and $P=P_\text{pch}$ diffusion time, for 1, 5, and 15 batches
	\item Krylov iterations to tols 1e-1 and 1e-6 vs diffusion parameter
	\item Krylov method convergence plot: $R$ vs $P_\text{pch}$ vs no preconditioner
	\item Krylov iterations to tols 1e-6 vs mesh size $h$, PCH vs no preconditioner (hold)
	\item true parameter (H)
	\item deterministic reconstruction (H)
	\item noisy measurements (1\% noise). $u|_\text{top}$ (H)
	\item recovered state at top (H)
	\item mesh scalability of PCH (CC) (H)
\end{itemize}

\begin{itemize}
	\item GLR vs PCH number of obs (Computational cost) (S)
	\item GLR vs PCH aspect ratio (CC) (S)
	\item turn on preconditioner after number of krylov iterations exceeds 15 in an iteration. Rebuild "as needed". (S)
\end{itemize}
